---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
**For demonstration purposes** - easy enough to turn into a CRAN-worthy package; let me know if you have interest

# forcer

`forcer` is a quickly assembled `htmlwidget` for Vasco Asturiano's [`react-force-graph`](https://github.com/vasturiano/react-force-graph).  The package is designed to work but also primarily to demonstrate how to use `reactR::scaffoldWidget` to create an `htmlwidget` from a `React` component.  Please see the tutorial [htmlwidgets with reactR](https://react-r.github.io/reactR/articles/intro_htmlwidgets.html) for the steps to go from `React` component to fully functioning `htmlwidget`. 

## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("react-R/forcer")
```

## Example

Here are some very quick examples to demonstrate the three types of force-directed graphs provided.

```{r example}
library(d3r)
library(igraph)
library(forcer)

# VR crashed my RStudio so open in real browser
options(viewer = NULL)

# 2D
forcer(
  data = d3r::d3_igraph(igraph::make_tree(60,3,mode="in")),
  forcetype = "ForceGraph2D",
  nodeColor = list("#0f0"),
  linkCurvature = 0.25
)
```

... and for 3d and a-frame VR ...

```{r eval=FALSE}
# 3D
forcer(
  data = d3r::d3_igraph(igraph::make_tree(60,3)),
  forcetype = "ForceGraph3D"
)

# VR
forcer(
  data = d3r::d3_igraph(igraph::make_tree(60,3)),
  forcetype = "ForceGraphVR"
)

```
